---
title: "Project 7"
author: "Symphony Hopkins"
date: "2022-12-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include = FALSE, echo = FALSE}
library(readr)
kc_house_data <- read_csv("~/Documents/Maryville_University/DSCI_502/kc_house_data.csv")
```

**1. Numerically summarize the price info by finding its minimum, maximum, range, mean, median, and the standard deviation of prices.**

-   The minimum price value is `r min(kc_house_data$price)`.
-   The maximum price value is `r max(kc_house_data$price)`.
-   The range of the price values is `r range(kc_house_data$price)`.
-   The mean price value is `r mean(kc_house_data$price)`.
-   The median price value is `r median(kc_house_data$price)`.
-   The standard deviation of the price values is `r sd(kc_house_data$price)`.

**2. Graphically summarize the following info:**

```{r, include = FALSE, echo = FALSE}
library(ggplot2)
```

a. Plot a histogram of prices.

```{r, echo = FALSE}
ggplot(data = kc_house_data, aes(x = price)) + geom_histogram() + ggtitle("Histogram of Prices") + xlab(" Prices") + ylab("Count")
```

b. Plot the box plot of prices against view.

```{r, echo = FALSE}
kc_house_data$view <- as.factor(kc_house_data$view)

ggplot(data=kc_house_data, aes(x=price, y=view)) + 
  geom_boxplot(aes(col= view), notch = TRUE) + ggtitle("Boxplot of Prices Against View") + xlab("Prices") + ylab("View")
```

c. Scatter plot of prices against sqft_living.

```{r, echo = FALSE}
ggplot(data = kc_house_data, aes(x = price, y=sqft_living))+geom_point() + geom_smooth() + ggtitle("Scatterplot of Prices Against Sqft Living") + xlab("Prices") + ylab("Sqft Living")
```

**3. Build the following linear models to forecast the price and recommend the best model to the management**

a. Forecast price using bedrooms, bathrooms and sqft_living.

```{r, echo = FALSE}
lm_result_1 <- lm(price ~ bedrooms + bathrooms + sqft_living, data= kc_house_data)

summary(lm_result_1)

```

b. Forecast the price using bedrooms, bathrooms and sqft_living and all the cross effects between them.

```{r, echo = FALSE}
lm_result_2 <- lm(price ~ (bedrooms + bathrooms + sqft_living)^3, data= kc_house_data)

summary(lm_result_2)
```

c. Forecast the price using bedrooms, bathrooms and sqft_living, waterfront and grade.

```{r, echo = FALSE}
lm_result_3 <- lm(price ~ bedrooms + bathrooms + sqft_living + waterfront + grade, data= kc_house_data)

summary(lm_result_3)
```

**Looking at the adjusted r-square scores from Models A, B, and C, we can see that Model C is the best model for the management.**



